### 2021-08-03 ch07_conclusion/conclusion.tex
Prepared document for publication

The analysis of future climate projections from numerical climate model
simulations is of paramount importance to assess future climate change under
different forcing scenarios. Since this involves metrics of public interest
like the allowable fossil fuel emissions to meet particular warming targets,
for example, the $1.5 \unit{\degreeCelsius}$ of the Paris Agreement
\autocite{UNFCCC2015}, research in this field of science is not only relevant
to climate scientists but also to policymakers and human society as a whole. In
the light of the large spread of climate sensitivity in the most recent
generation of climate models from \acs{CMIP}6, which has been demonstrated in
\cref{ch:04:papers_ecs_tcr_assessment}, a careful statistical evaluation and
refinement of the output of multi-model climate projections is as relevant as
ever. This thesis quantifies uncertainties in climate model projections,
presents the evaluation of established methods to reduce these uncertainties in
a new climate model ensemble, and finally introduces a novel alternative
technique based on supervised \ac{ML}.

To answer the \lcnamecrefs{enum:01:question_1} posed in
\cref{sec:01:key_science_questions} and to ensure a consistent evaluation of
the participating climate model ensembles in this thesis, the \ac{ESMValTool}
is used, an open-source community diagnostics and performance metrics tool for
the routine evaluation of \acp{ESM}. All analyses shown in this thesis are
performed with the \ac{ESMValTool}. Apart from that, further substantial
changes and additions to the code base of the tool have been implemented as
part of this thesis (see \cref{ch:03:esmvaltool}), which led to co-authorship
in the technical and scientific documentation of the \ac{ESMValTool}
\autocite{Eyring2020, Lauer2020, Righi2020, Weigel2020}. Since the open-source
tool is freely available, the code that has been implemented as part of this
thesis is beneficial for the entire scientific community.

>>>>

The analysis of future climate projections from numerical climate model
simulations is of paramount importance to assess future climate change under
different forcing scenarios. Since this involves metrics of public interest
like the allowable fossil fuel emissions to meet particular warming targets,
for example, the $1.5 \unit{\degreeCelsius}$ of the Paris Agreement
\autocite{UNFCCC2015}, research in this field of science is not only relevant
to climate scientists but also to policymakers and human society as a whole. In
light of the large spread of climate sensitivity in the most recent generation
of climate models from \acs{CMIP}6, which has been demonstrated in
\cref{ch:04:papers_ecs_tcr_assessment}, a careful statistical evaluation and
refinement of the output of multi-model climate projections is as relevant as
ever. This thesis quantifies uncertainties in climate model projections,
presents the evaluation of established methods to reduce these uncertainties in
a new climate model ensemble, and finally introduces a novel alternative
technique based on supervised \ac{ML}.

To answer the \lcnamecrefs{enum:01:question_1} posed in
\cref{sec:01:key_science_questions} and to ensure a consistent evaluation of
the participating climate model ensembles in this thesis, the \ac{ESMValTool}
is used, an open-source community diagnostics and performance metrics tool for
the routine evaluation of \acp{ESM}. All analyses shown in this thesis are
performed with the \ac{ESMValTool}. Apart from that, further substantial
changes and additions to the code base of the tool have been implemented as
part of this thesis (see \cref{ch:03:esmvaltool}), which led to co-authorship
in the technical and scientific documentation of the \ac{ESMValTool}
\autocite{Eyring2020, Lauer2020, Righi2020, Weigel2021}. Since the open-source
tool is freely available, the code that has been implemented as part of this
thesis is beneficial for the entire scientific community.

### 2021-08-03 end_acknowledgments/acknowledgments.tex
Prepared document for publication

First of all, I would like to express my sincere gratitude to my supervisor and
primary examiner, \Prof{} \Dr{} Veronika Eyring. Without her continuous
support, advice, enthusiasm, expertise, and patience, this \PhD{} project would
not have been possible. I further thank her for providing me the opportunity to
visit many international conferences, which allowed me to meet amazing people
and collaborate with colleagues from all around the world.

I am grateful to my second examiner, \Prof{} \Dr{} Pierre Gentine, for his
great advice and feedback on my work.

My sincere thanks go to all my co-authors, namely \Prof{} \Dr{} Gustau
Camps-Valls, \Prof{} \Dr{} Veronika Eyring, \Prof{} \Dr{} Pierre
Friedlingstein, \Prof{} \Dr{} Pierre Gentine, \Dr{} Axel Lauer, \Prof{} \Dr{}
Markus Reichstein, and \Prof{} \Dr{} Steven Sherwood, for sharing their
expertise, their advice, and helpful comments on my studies.

>>>>

First of all, I would like to express my sincere gratitude to my supervisor and
primary examiner, \ThePrimaryExaminer{}. Without her continuous support,
advice, enthusiasm, expertise, and patience, this \PhD{} project would not have
been possible. I further thank her for providing me the opportunity to visit
many international conferences, which allowed me to meet amazing people and
collaborate with colleagues from all around the world.

I am grateful to my secondary examiner, \TheSecondaryExaminer{}, for his great
advice and feedback on my work.

My sincere thanks go to all my co-authors, namely \Prof{} \Dr{} Gustau
Camps-Valls, \ThePrimaryExaminer{}, \Prof{} \Dr{} Pierre Friedlingstein,
\TheSecondaryExaminer{}, \Dr{} Axel Lauer, \Prof{} \Dr{} Markus Reichstein, and
\Prof{} \Dr{} Steven Sherwood, for sharing their expertise, their advice, and
helpful comments on my studies.
